Online {\IterComp}

### 2017-09-16 results.tex
tiny error

For a few of the benchmarks, relaxation unexpectedly introduces additional overhead. This is counter-intuitive since relaxation leads to
less computational work. In these cases, relaxation did not manage to remove high frequency probes, so we did not benefit significantly.
On the other, the probes that were removed affected how \texttt{-O3} optimized the surrounding code, in some cases blocking useful
optimizations that were applied originally. This resulted in slightly slower code.
%For example, some of the optimizations that make use of this built-in cost model
%and also alter the CFG are: loop-unrolling, function inlining, and
%simplifications of the CFG.
%These changes in the program's CFGs may affect other compiler optimizations and
%also possibly in hardware performance, for example affecting the instruction
%caching.

>>>>

For a few of the benchmarks, relaxation unexpectedly introduces additional overhead. This is counter-intuitive since relaxation leads to
less computational work. In these cases, relaxation did not manage to remove high frequency probes, so we did not benefit significantly.
On the other hand, the probes that were removed affected how \texttt{-O3} optimized the surrounding code, in some cases blocking useful
optimizations that were applied originally. This resulted in slightly slower code.
%For example, some of the optimizations that make use of this built-in cost model
%and also alter the CFG are: loop-unrolling, function inlining, and
%simplifications of the CFG.
%These changes in the program's CFGs may affect other compiler optimizations and
%also possibly in hardware performance, for example affecting the instruction
%caching.
